Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-11-25 paper/main.tex
reworking up to artist
nlab pullback bundle

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repeation of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \Gamma(\dbase, \dtotal) \xrightarrow{\vindex^*} \Gamma(\gbase, \vindex^*\dtotal)
\end{equation}
to generate a set of equivalent sections over the graphic $\Gamma(\gtotal, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space $\sheaf: \mathcal{\gbase^{op}} \rightarrow \Gamma(\gtotal, \vindex^*{\dtotal})$ which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}: \mathcal{\gbasec^{op}} \rightarrow \textcolor{section}{\bm{Set}}
\end{equation}

>>>>

\begin{figure}[h!]
  \includegraphics[width=\columnwidth]{pullback.png}
  \label{fig:artist:pushforward_xi}
  \caption{The map $\vindex^*$ is a map from a repeation of the 1D fiber over every point $\dbasepoint \in \dbase$ in data space, turning the fiber into a 2D plane of repeating values over the corresponding region $\dbasepoint = \vindex(\gbasepoint)$ in the graphic space \gbase. }
\end{figure}
Since there is a mapping from the graphic space to the total bundle $\dsection \circ \vindex: \gbase \rightarrow \dtotal$, the mapping $\vindex$ can be pulled through the composition such that there is a map $\vindex^*$ between a total space over graphics $\vindex^*\dtotal$ and its equivalent space over data $\dtotal$.  As illustrated in the example given in \autoref{fig:artist:pushforward_xi}, a bundle $\dtotal$ over a point $\dbasepoint \in \dbase$ is pulled back through \vindex\ \cite{nlab:pullback_bundle} such that it is copied over every point in the corresponding region in graphic space $\vindex(\gbasepoint) = \dbasepoint, \gbasepoint \subset \gbase$. The pullback $\vindex^*$ can then be composed with the elements of the set of sections 
\begin{equation}
  \label{eq:artist:data_gamma_pullback}
 \Gamma(\dbase, \dtotal) \xrightarrow{\vindex^*} \Gamma(\gbase, \vindex^*\dtotal)
\end{equation}
to generate a set of equivalent sections over the graphic $\Gamma(\gtotal, \vindex^*{\dtotal})$. As a consequence of \autoref{eq:artist:data_gamma_pullback}, there exists a data sheaf over graphic space $\sheaf: \mathcal{\gbase^{op}} \rightarrow \Gamma(\gtotal, \vindex^*{\dtotal})$ which is equivalent to 
\begin{equation}
  \label{eq:artist:data_pullback_sheaf}
  \sheafc_{\vindexc^*}: \mathcal{\gbasec^{op}} \rightarrow \textcolor{section}{\bm{Set}}
\end{equation}
